---
title: "Mercari EDA"
author: "Kazim Anil EREN"
date: "3 Aralık 2017"
output: html_document
---
This Markdown file is generated to describe the work done for the **Mercari Pricing** Case.

## Required Libraries & Functions

```{r results = 'hide', message = FALSE} 
rm(list = ls()); gc()
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library("stringr")
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
```

## Data Input

```{r results = 'hide'}
test  <- fread(input = "test.tsv", sep = "\t")
train <- fread(input = "train.tsv", sep = "\t")

train[, ':='(item_description = as.factor(tolower(item_description)),
						 category_name    = as.factor(tolower(category_name)),
						 name             = as.factor(tolower(name)))]
train <- train[, `:=`(H1 = str_split_fixed(string = category_name, pattern = "/", n = 3)[,1],
			 							  H2 = str_split_fixed(string = category_name, pattern = "/", n = 3)[,2],
			  						  H3 = str_split_fixed(string = category_name, pattern = "/", n = 3)[,3])]
train[, shipping := as.factor(shipping)]
train[, item_condition_id := as.factor(item_condition_id)]
train[, category_name := NULL]
train <- train[price != 0] # No item can be sold for no fee.
train[, ':='(desc_len = str_length(item_description),
						 desc_cnt = str_count(item_description))]
source("categorize.R")
train <- merge(train, train[, .(NH3 = .N), .(H1, H2, H3)], by = c("H1", "H2", "H3"))
train <- merge(train, train[NH3 < 1000, .(NH2 = .N), .(H1, H2)], by = c("H1", "H2"))
train <- merge(train, train[NH2 < 1000, .(NH1 = .N), .(H1)], by = c("H1"))
train[, category := categorize(H1, H2, H3, NH2, NH3)]

test[, ':='(item_description = as.factor(tolower(item_description)),
		 			  category_name    = as.factor(tolower(category_name)),
						name             = as.factor(tolower(name)))]
test  <- test[, `:=`(H1 = str_split_fixed(string = category_name, pattern = "/", n = 3)[,1],
										 H2 = str_split_fixed(string = category_name, pattern = "/", n = 3)[,2],
										 H3 = str_split_fixed(string = category_name, pattern = "/", n = 3)[,3])]
test[, shipping := as.factor(shipping)]
test[, item_condition_id := as.factor(item_condition_id)]
test[, category_name := NULL]
test[, ':='(desc_len = str_length(item_description),
						desc_cnt = str_count(item_description))]

test <- merge(test, train[, .N ,.(H1, H2, H3, NH2, NH3)][, 1:5], by = c("H1", "H2", "H3"))
test[, category := categorize(H1, H2, H3, NH2, NH3)]

train[, `:=`(NH1 = NULL, NH2 = NULL, NH3 = NULL)]
test[, `:=`(NH1 = NULL, NH2 = NULL, NH3 = NULL)]
rm(categorize)
```

## Exploraty Data Analysis: Basics

There are `r length(unique(train$brand_name))` unique different brands.

Also 5 different conditions, "1" is the most frequent, then the rest as numeric order. It is thought that. 1 is brand new / unused and the rest are in decreasing order.
```{r echo = FALSE}
train[, .N, .(item_condition_id)][order(item_condition_id)]
```

```{r echo = FALSE}
ggplot(data = train[price < 100], aes(x = item_condition_id, y = price)) + geom_boxplot()
```

Let's see the summary statistics for the price vector as well.
```{r echo = FALSE}
summary(train$price)
```

```{r echo = FALSE}
hist(train[price < 100]$price)
```

Categories may have significant effect on prices. There are `r train[, .N, .(H1, H2, H3)][, .N]` different H3 level categories under `r train[, .N, .(H1)][, .N]` different H1 level categories and `r train[, .N, .(H1, H2)][, .N]` H2 level categories.
```{r echo = FALSE}
ggplot(data = train, aes(x = H1, y = price)) + geom_boxplot()
```

Let's focus on the prices below 100 since there are many outliers.
```{r echo = FALSE}
ggplot(data = train[price < 100], aes(x = H1, y = price)) + geom_boxplot()
```

```{r echo = FALSE}
x <- unique(train$H1)
for(i in 1:length(x)){
	print(paste0("Next price summary is for ", x[i], "H1 group."))
	print(summary(train[H1 == x[i]]$price))
}
rm(x)
```


Next, lets check if free-shipping can affect the prices. There are `r train[shipping == 1, .N, .(shipping)][,2]$N` products that has free-shipping and `r train[shipping == 0, .N, .(shipping)][,2]$N` otherwise.

```{r echo = FALSE}
ggplot(data = train[price < 100], aes(x = shipping, y = price)) + geom_boxplot()
```

## Text Mining Process

```{r eval = FALSE}
train_name <- Corpus(VectorSource(train$name))
# train_desc <- Corpus(VectorSource(train$item_description))

train_name <- tm_map(train_name, content_transformer(tolower)) # Convert the text to lower case
# train_name <- tm_map(train_name, removeNumbers) # Remove numbers
train_name <- tm_map(train_name, removeWords, stopwords("english")) # Remove english common stopwords
# train_name <- tm_map(train_name, removeWords, c("blabla1", "blabla2")) # Remove your own stop word: specify your stopwords as a character vector
train_name <- tm_map(train_name, removePunctuation) # Remove punctuations
train_name <- tm_map(train_name, stripWhitespace) # Eliminate extra white spaces
# train_name <- tm_map(train_name, stemDocument) # Text stemming. 
```


```{r}
wordcloud()
```
