---
title: "Mercari EDA"
author: "Kazim Anil EREN"
date: "1 Aralık 2017"
output: html_document
---
This Markdown file is generated to describe the work done for the **Mercari Pricing** Case.

## Required Libraries & Functions

Şimdilik açık bıraktım, sonrasında echo = FALSE, seçeneğiyle kodların görünmesini engelleyebilir. 
Bu kısma yorumlarımızı yazabiliriz.

```{r results = 'hide', message = FALSE} 
rm(list = ls()); gc()
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library("stringr")
toSpace <- content_transformer(function (x , pattern ) gsub(pattern, " ", x))
```

## Data Input

```{r results = 'hide'}
test  <- fread(input = "test.tsv", sep = "\t")
train <- fread(input = "train.tsv", sep = "\t")
test  <- test[, `:=`(H1 = str_split_fixed(string = category_name, pattern = "/", n = 3)[,1],
										 H2 = str_split_fixed(string = category_name, pattern = "/", n = 3)[,2],
										 H3 = str_split_fixed(string = category_name, pattern = "/", n = 3)[,3])]
train <- train[, `:=`(H1 = str_split_fixed(string = category_name, pattern = "/", n = 3)[,1],
			 							  H2 = str_split_fixed(string = category_name, pattern = "/", n = 3)[,2],
			  						  H3 = str_split_fixed(string = category_name, pattern = "/", n = 3)[,3])]
```

## Exploraty Data Analysis: Basics

There are `r train[shipping == 1, .N, .(shipping)][,2]$N` products that has free-shipping and `r train[shipping == 0, .N, .(shipping)][,2]$N` otherwise.
There are `r length(unique(train$brand_name))` unique different brands.

There are also 5 different conditions, "1" is the most frequent, then the rest as numeric order. 
It is thought that. 1 is brand new / unused and the rest are in decreasing order.
```{r echo = FALSE}
train[, .N, .(item_condition_id)][order(item_condition_id)]
```

## Text Mining Process

```{r eval = FALSE}
# train_name <- Corpus(VectorSource(train$name))
# train_desc <- Corpus(VectorSource(train$item_description))
train_name <- tm_map(train_name, content_transformer(tolower)) # Convert the text to lower case
# train_name <- tm_map(train_name, removeNumbers) # Remove numbers
train_name <- tm_map(train_name, removeWords, stopwords("english")) # Remove english common stopwords
# train_name <- tm_map(train_name, removeWords, c("blabla1", "blabla2")) # Remove your own stop word: specify your stopwords as a character vector
train_name <- tm_map(train_name, removePunctuation) # Remove punctuations
train_name <- tm_map(train_name, stripWhitespace) # Eliminate extra white spaces
# train_name <- tm_map(train_name, stemDocument) # Text stemming
```

```{r}
# wordcloud(train_name)
```

